Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-08-27 bbbq_article.tex
Processed submat feedback, thanks @fransbianchi
Link to Dryad

All code is archived at \url{http://github.com/richelbilderbeek/someplace},
with DOI \url{https://doi.org/12.3456/zenodo.1234567}.

@@

However, in this study, an MHC binder is defined as a peptide within a \emph{proteome} in which it is found, that is among the peptides with the 2\% lowest IC50 values.
Subsection \ref{subsec:ic50s_per_haplotype} shows the IC50 values
for a binder per haplotype. We believe that our revised definition is more correct, as it overcomes bias from proteins with very low numbers of peptides and/or MHC-predicted binders.

>>>>

All code, intermediate and final results are archived at 
Dryad at \url{https://doi.org/10.5061/dryad.fn2z34tv1}.

@@

However, in this study, an MHC binder is defined as a peptide within a \emph{proteome} in which it is found, that is among the peptides with the 2\% lowest IC50 values.
Subsection \ref{subsec:ic50s_per_haplotype} shows the IC50 values
for a binder per haplotype.
